Articles of Association of London Hackspace Ltd.

### 2011-07-20 constitution/articles-body.tex
Specify a quorum of 10

\item
  \begin{enumerate}
  \item
    No business shall be transacted at any general meeting unless a
    quorum is present.
  \item
    A quorum is:
    \begin{enumerate}
    \item x members present in person or by proxy and entitled to vote upon
      the business to be conducted at the meeting; or
    \item
      one tenth of the total membership at the time
    \end{enumerate}
  \item
    The authorised representative of a member organisation shall be
    counted in the quorum.
  \end{enumerate}

\item
  \begin{enumerate}
  \item
    If :
    \begin{enumerate}
    \item
      a quorum is not present within half an hour from the time appointed
      for the meeting; or
    \item
      during a meeting a quorum ceases to be present; the meeting shall
      be adjourned to such time and place as the directors shall
      determine.
    \end{enumerate}
  \item
    The directors must reconvene the meeting and must give at least
    seven clear days' notice of the reconvened meeting stating the
    date, time and place of the meeting.
  \item
    If no quorum is present at the reconvened meeting within fifteen
    minutes of the time specified for the start of the meeting the
    members present in person or by proxy at that time shall constitute
    the quorum for that meeting.
  \end{enumerate}
\item

@@

\item
  \begin{enumerate}
  \item
    A director must be a natural person aged 16 years or older.
  \item
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article \ref{director-cease}.
  \end{enumerate}
\item
  The number of directors shall be not less than three but (unless
  otherwise determined by ordinary resolution) shall not be subject
  to any maximum.

@@

\section{Seal}

\item
  If the charity has a seal it must only be used by the authority of
  the directors or of a committee of directors authorised by the
  directors. The directors may determine who shall sign any
  instrument to which the seal is affixed and unless otherwise so
  determined it shall be signed by a director and by the secretary
  (if any) or by a second director.

>>>>

\item
  \begin{enumerate}
  \item
    No business shall be transacted at any general meeting unless a
    quorum is present.
  \item
    A quorum is:
    \begin{enumerate}
    \item 10 members present in person or by proxy and entitled to vote upon
      the business to be conducted at the meeting; or
    \item
      one tenth of the total membership at the time
    \end{enumerate}
  \item
    The authorised representative of a member organisation shall be
    counted in the quorum.
  \end{enumerate}

\item
  \begin{enumerate}
  \item
    If:
    \begin{enumerate}
    \item
      a quorum is not present within half an hour from the time appointed
      for the meeting; or
    \item
      during a meeting a quorum ceases to be present; the meeting shall
      be adjourned to such time and place as the directors shall
      determine.
    \end{enumerate}
  \item
    The directors must reconvene the meeting and must give at least
    seven clear days' notice of the reconvened meeting stating the
    date, time and place of the meeting.
  \item
    If no quorum is present at the reconvened meeting within fifteen
    minutes of the time specified for the start of the meeting the
    members present in person or by proxy at that time shall constitute
    the quorum for that meeting.
  \end{enumerate}
\item

@@

\item
  \begin{enumerate}
    A director must be a natural person aged 16 years or older.
  \item
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article \ref{director-cease}.
  \end{enumerate}
\item
  The number of directors shall be not less than three but (unless
  otherwise determined by ordinary resolution) shall not be subject
  to any maximum.

@@
